---
title: "Tutorial"
author: "Jaila Golden"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To install this package

```{r, eval=FALSE}
devtools::install_github("jailagolden/Golden.package")
```

Now, load the package...

```{r, echo=FALSE}
library(Golden.package)
```


## Querying Organisms 

This function queries an organism and obtains the GPS coordinates for the organism. 
You could use this to obtain information about where the Red-Billed Quelea is found. 
It uses rgbif package to obtain the taxon key for the bird and will get the occurences of the bird. It will clear any data without a specific geographical location value. The function will save the data into a dataframe. 
I was trying to make the user input the organism's scientific name but got some trouble doing so in this function. So, the only organism you could search for is the Red-Billed Quelea. I chose this as it is available all over Africa and has a lot of data.

_Organism's Name: Quela quela_
_Taxon Key: 2493987_

```{r, eval=FALSE}
Organism()

